### 2024-08-16 README.Rmd
I saw the best minds of my generation destroyed by madness

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```

>>>>

Here it is:
```{r}
# install.packages("sdmtools", repos = "https://idem-lab.r-universe.dev")
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```
